\bf The EPEC Model

### 2021-08-29 Documentation/EPEC_Model.tex
Fully operational non-interpolating OMFIT version

The quantity ${\mit\Sigma}_k'$ is
defined as
\begin{equation}
{\mit\Sigma}_k' = \lim_{\delta\rightarrow 0}\left[\left.\frac{r\,\psi'}{\psi}\right|_{r_k-\delta}+ \left.\frac{r\,\psi'}{\psi}\right|_{r_k+\delta}
-2\,A_k\,(1+\ln\delta)\right],
\end{equation}
where $\psi(r)$ is the solution of 
\begin{equation}
\frac{d^{\,2}\psi}{dr^{\,2}}+ \frac{1}{r}\,\frac{d\psi}{dr}-\frac{m^{\,2}}{r^{\,2}}\,\psi - \frac{\hat{J}_\phi'\,\psi}{r\,(1/q-n/m_k)}=0
\end{equation}
that is well=behaved at $r=0$, and satisfies $r\,\psi'/\psi = -m$ at $r=r_{100}$. Here, $\psi'\equiv d\psi/dr$.

@@

The total change in the plasma pressure interior to the $j$th resonant surface due to the temperature and
density flattening at the various resonant surfaces (assuming that the pressure at the LCFS is fixed) is
\begin{align}
{\mit\Delta}P_j &=\sum_{k=j,K} 
\left\{(F_1+F_3)\,\delta_{n_e\,k}+ F_2\,\delta_{T_e\,k}+F_4\,\delta_{T_i\,k} + (F_5+F_7)\,\delta_{n_e\,k}\,\overline{W}_k^{\,2}
\right.\nonumber\\[0.5ex]
&\phantom{++}\left.+F_6\, \delta_{T_e\,k}\,\overline{W}_k^{\,2}+ F_8\,\delta_{T_i\,k}\,\overline{W}_k^{\,2}+ (F_9+F_{11})\,\delta_{n_e\,k}^{\,3}
+ F_{10}\,\delta_{T_e\,k}^{\,3}+ F_{12}\,\delta_{T_i\,k}^{\,3}\right\}_{r_k},
\end{align}
where
\begin{align}
F_1 &=\frac{dn_e}{d{\mit\Psi}_N}\,T_e,\\[0.5ex]
F_2 &=\frac{dT_e}{d{\mit\Psi}_N}\,n_e,\\[0.5ex]
F_3 &=\frac{dn_i}{d{\mit\Psi}_N}\,T_i,\\[0.5ex]
F_4 &=\frac{dT_i}{d{\mit\Psi}_N}\,n_i,\\[0.5ex]
F_5&= -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right),\\[0.5ex]
F_6&= -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\,n_e\right),\\[0.5ex]
F_7& =-\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}\,T_i\right),\\[0.5ex]
F_8& =-\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\,n_i\right),\\[0.5ex]
F_9&=\frac{T_e}{24}\,\frac{d^{\,3}n_e}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
F_{10}&=\frac{n_e}{24}\,\frac{d^{\,3}T_e}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
F_{11}&=\frac{T_i}{24}\,\frac{d^{\,3}n_i}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
F_{12}&=\frac{n_i}{24}\,\frac{d^{\,3}T_i}{d{\mit\Psi}_N^{\,3}},
\end{align} 
and we have neglected the impurity ion pressure.

>>>>

The quantity ${\mit\Sigma}_k'$ is
defined as
\begin{equation}
{\mit\Sigma}_k' = \lim_{\delta\rightarrow 0}\left[\left.\frac{r\,\psi'}{\psi}\right|_{r_k-\delta}+ \left.\frac{r\,\psi'}{\psi}\right|_{r_k+\delta}
-2\,A_k\,(1+\ln\delta)\right],
\end{equation}
where $\psi(r)$ is the solution of 
\begin{equation}
\frac{d^{\,2}\psi}{dr^{\,2}}+ \frac{1}{r}\,\frac{d\psi}{dr}-\frac{m^{\,2}}{r^{\,2}}\,\psi - \frac{\hat{J}_\phi'\,\psi}{r\,(1/q-n/m_k)}=0
\end{equation}
that is well-behaved at $r=0$, and satisfies $r\,\psi'/\psi = -m$ at $r=r_{100}$. Here, $\psi'\equiv d\psi/dr$.

@@

The total change in the plasma pressure interior to the $j$th resonant surface due to the temperature and
density flattening at the various resonant surfaces (assuming that the pressure at the LCFS is fixed) is
\begin{align}
{\mit\Delta}P_j &=\sum_{k=j,K} 
\left\{(F_1+F_3)\,\delta_{n_e\,k}+ F_2\,\delta_{T_e\,k}+F_4\,\delta_{T_i\,k} + (F_5+F_7)\,\delta_{n_e\,k}\,\overline{W}_k^{\,2}
\right.\nonumber\\[0.5ex]
&\phantom{++}\left.+F_6\, \delta_{T_e\,k}\,\overline{W}_k^{\,2}+ F_8\,\delta_{T_i\,k}\,\overline{W}_k^{\,2}+ (F_9+F_{11})\,\delta_{n_e\,k}^{\,3}
+ F_{10}\,\delta_{T_e\,k}^{\,3}+ F_{12}\,\delta_{T_i\,k}^{\,3}\right\}_{r_k},
\end{align}
where
\begin{align}
F_1 &=\frac{dn_e}{d{\mit\Psi}_N}\,T_e,\\[0.5ex]
F_2 &=\frac{dT_e}{d{\mit\Psi}_N}\,n_e,\\[0.5ex]
F_3 &=\frac{dn_i}{d{\mit\Psi}_N}\,T_i,\\[0.5ex]
F_4 &=\frac{dT_i}{d{\mit\Psi}_N}\,n_i,\\[0.5ex]
F_5&= -\frac{A_2}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right),\\[0.5ex]
F_6&= -\frac{A_2}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\,n_e\right),\\[0.5ex]
F_7& =-\frac{A_2}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}\,T_i\right),\\[0.5ex]
F_8& =-\frac{A_2}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\,n_i\right),\\[0.5ex]
F_9&=\frac{T_e}{24}\,\frac{d^{\,3}n_e}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
F_{10}&=\frac{n_e}{24}\,\frac{d^{\,3}T_e}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
F_{11}&=\frac{T_i}{24}\,\frac{d^{\,3}n_i}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
F_{12}&=\frac{n_i}{24}\,\frac{d^{\,3}T_i}{d{\mit\Psi}_N^{\,3}},
\end{align} 
and we have neglected the impurity ion pressure.
